---
title: "psyTeachR Google Analytics"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  out.width = "100%"
)
library(tidyverse)
library(patchwork)
library(DT)
theme_set(theme_minimal())
Sys.setenv("VROOM_CONNECTION_SIZE" = 200000)
options(scipen = 5)
```



```{r}
# import data

# !Remember to set Search to "Page path + query string and screen" 
# and add "Hostname" before downloading data

# files are structured poorly, so search for the full header 

headers <- "Page path + query string and screen class,Hostname,Views,Users,New users,Views per user,Average engagement time,Unique user scrolls,Event count,Conversions,Total revenue"

files <- list.files("data", full.names = TRUE)

datalist <- list()

for (file in files) {
  #cat(file, "\n")
  lines <- readLines(file)
  skip <- grepl(headers, lines, fixed = TRUE) %>% which() - 1
  
  lines[grepl("Page path", lines, fixed = TRUE) %>% which()]
  
  start_date <- gsub("# Start date: ", "", lines[8], fixed = TRUE) %>%
    lubridate::as_date()
  end_date <- gsub("# End date: ", "", lines[9], fixed = TRUE) %>%
    lubridate::as_date()

  datalist[[file]] <- read_csv(file, 
                   skip = skip, 
                   show_col_types = FALSE) %>%
    mutate(start_date = start_date, end_date = end_date)
}

data <- do.call(bind_rows, datalist)

```

Data from `r min(data$start_date)` to `r max(data$end_date)`


```{r}
data2 <- data %>%
  filter(grepl("psyteachr", Hostname)) %>%
  separate(1, into = c("url", "query"), 
           sep = "\\?", 
           fill = "right") %>%
  separate(url, into = c("base", "book", "page"), 
           sep = "/", 
           fill = "right",
           extra = "merge") %>%
  select(-base) %>%
  mutate(book = ifelse(book %in% c("", "index.html"), "_psyTeachR_", book)) %>%
  filter(!is.na(book))
```

```{r}
views_by_book <- data2 %>%
  group_by(book) %>%
  summarise(views = sum(Views),
            pages = n_distinct(page), 
            total_hours = sum(Views * `Average engagement time`),
            .groups = "drop") %>%
  mutate(total_hours = round(total_hours/60/60, 1)) %>%
  arrange(desc(views))

total_views <- sum(views_by_book$views) %>% format(big.mark = ",", )
th <- sum(views_by_book$total_hours)
hours <- round(th) %>% format(big.mark = ",", )
days <-  round(th/24)
years <- round(th/24/365.25, 1)
```

PsyTeachR books have had `r total_views` page views. People have spent `r hours` hours on psyTeachR books. That's about `r days` days, or `r years` years!


## Views by book

```{r}
DT::datatable(views_by_book)
```



```{r}
book_by_week <- data2 %>%
  group_by(book, start_date) %>%
  summarise(users = sum(Users),
            views = sum(Views),
            .groups = "drop")

book_order <- book_by_week %>%
  group_by(book) %>%
  summarise(total = sum(views),
            .groups = "drop") %>%
  arrange(book) %>%
  pull(book)

book_by_week$book <- factor(book_by_week$book, levels = book_order)
```



```{r}
# plotting function
week_plot <- function(data, col, min = 1, max = 1e5) {
  data %>%
    group_by(book) %>%
    filter(max(.data[[col]]) >= min, max(.data[[col]]) < max) %>%
    ungroup() %>%
    ggplot(aes(x = start_date, y = .data[[col]])) +
    geom_point(size = 2, color = "dodgerblue") +
    geom_line(size = 1, color = "dodgerblue3") +
    scale_x_date(name = "",
                 date_breaks = "1 week",
                 date_label = "%b-%d") +
    facet_wrap(~book, ncol = 1) +
    expand_limits(y=0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```


## Views per week {.tabset}

```{r views-plots, results='asis'}
invisible({
  book_by_week %>% 
    dplyr::group_split(book) %>% 
    purrr::imap(., ~{
      # create tabset for each group 
      bookname <- as.character(unique(..1$book))
      cat('\n### ', bookname, '   \n\n')
      p <- week_plot(..1, "views")
      print(p)
      cat('\n')
    })
})

```


## Users per week  {.tabset}

```{r users-plots, results='asis'}
invisible({
  book_by_week %>% 
    dplyr::group_split(book) %>% 
    purrr::imap(., ~{
      # create tabset for each group 
      bookname <- as.character(unique(..1$book))
      cat('\n### ', bookname, '   \n\n')
      p <- week_plot(..1, "users")
      print(p)
      cat('\n')
    })
})

```


## Non-psyTeachR books

The Google Analytics is in our bookdown template, so it is sometimes used by others who have used our book template or forked our books on github. They are listed below.

```{r}
data %>%
  filter(!grepl("psyteachr", Hostname)) %>%
  separate(1, into = c("url", "query"), 
           sep = "\\?", 
           fill = "right") %>%
  separate(url, into = c("base", "book", "page"), 
           sep = "/", 
           fill = "right",
           extra = "merge") %>%
  group_by(Hostname, book) %>%
  summarise(views = sum(Views),
            pages = n_distinct(page), 
            total_hours = sum(Views * `Average engagement time`),
            .groups = "drop") %>%
  mutate(total_hours = round(total_hours/60/60, 1)) %>%
  arrange(desc(views)) %>%
  DT::datatable()
```


